First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2019-10-10 MY_PUBLICATIONS/PRL/prl.tex
add deuteron articles
update PRL

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version xx as of \today}
\leftline{Primary authors: Carlos Yero}
\leftline{To be submitted to (PRL, PRD-RC, PRD, PLB; choose one.)}
\leftline{Comment to {\tt d0-run2eb-nnn@fnal.gov} by xxx, yyy}
\centerline{\em D\O\ INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

\title{Template for PRL/PRD Papers}
\input author_list.tex       % D0 authors (remove the first 3 lines
                             % of this file prior to submission, they
                             % contain a time stamp for the authorlist)
                             % (includes institutions and visitors)
\date{\today}

\begin{abstract}
An article usually includes an abstract, a concise summary of the work
covered at length in the main body of the article. It is used for
secondary publications and for information retrieval purposes.
For PRL, the rule of thumb is that the abstract should be less than
8 lines and the text (excluding authors, abstract but including tables,
figures and references) should be less than 4 pages (leave about 20 lines
empty on page 4) in two-column format.
PRL and PRD papers have to have PACS (Phsyics and Astronomy Classification
Scheme) numbers. Please see {\tt http://www.aip.org/pacs/} for the numbers
relevant to your paper. A set of standard references can be found at the
end of this example paper.
\end{abstract}

@@

\begin{table}
\caption{\label{tab:table1}This is a narrow table which fits into a
narrow column when using \texttt{twocolumn} formatting. Note that
REV\TeX~4 adjusts the intercolumn spacing so that the table fills the
entire width of the column. Table captions are numbered
automatically. This table illustrates left-aligned, centered, and
right-aligned columns.  }
\begin{ruledtabular}
\begin{tabular}{lcr}
Left\footnote{Note a.}&Centered\footnote{Note b.}&Right\\
\hline
1 & 2 & 3\\
10 & 20 & 30\\
100 & 200 & 300\\
\end{tabular}
\end{ruledtabular}
\end{table}

\begin{table}
\caption{\label{tab:table2}A table with more columns still fits
properly in a column. Note that several entries share the same
footnote. Inspect the \LaTeX\ input for this table to see
exactly how it is done.}
\begin{ruledtabular}
\begin{tabular}{cccccccc}
 &$r_c$ (\AA)&$r_0$ (\AA)&$\kappa r_0$&
 &$r_c$ (\AA) &$r_0$ (\AA)&$\kappa r_0$\\
\hline
Cu& 0.800 & 14.10 & 2.550 &Sn\footnotemark[1]
& 0.680 & 1.870 & 3.700 \\
Ag& 0.990 & 15.90 & 2.710 &Pb\footnotemark[2]
& 0.450 & 1.930 & 3.760 \\
Au& 1.150 & 15.90 & 2.710 &Ca\footnotemark[3]
& 0.750 & 2.170 & 3.560 \\
Mg& 0.490 & 17.60 & 3.200 &Sr\footnotemark[4]
& 0.900 & 2.370 & 3.720 \\
Zn& 0.300 & 15.20 & 2.970 &Li\footnotemark[2]
& 0.380 & 1.730 & 2.830 \\
Cd& 0.530 & 17.10 & 3.160 &Na\footnotemark[5]
& 0.760 & 2.110 & 3.120 \\
Hg& 0.550 & 17.80 & 3.220 &K\footnotemark[5]
&  1.120 & 2.620 & 3.480 \\
Al& 0.230 & 15.80 & 3.240 &Rb\footnotemark[3]
& 1.330 & 2.800 & 3.590 \\
Ga& 0.310 & 16.70 & 3.330 &Cs\footnotemark[4]
& 1.420 & 3.030 & 3.740 \\
In& 0.460 & 18.40 & 3.500 &Ba\footnotemark[5]
& 0.960 & 2.460 & 3.780 \\
Tl& 0.480 & 18.90 & 3.550 & & & & \\
\end{tabular}
\end{ruledtabular}
\footnotetext[1]{Here's the first, from Ref.~\onlinecite{pdg}.}
\footnotetext[2]{Here's the second.}
\footnotetext[3]{Here's the third.}
\footnotetext[4]{Here's the fourth.}
\footnotetext[5]{And etc.}
\end{table}

\begin{table*}
\caption{\label{tab:table3}This is a wide table that spans the page
width in \texttt{twocolumn} mode. It is formatted using the
\texttt{table*} environment. It also demonstates the use of
\textbackslash\texttt{multicolumn} in rows with entries that span
more than one column.}
\begin{ruledtabular}
\begin{tabular}{ccccc}
 &\multicolumn{2}{c}{$D_{4h}^1$}&\multicolumn{2}{c}{$D_{4h}^5$}\\
 Ion&1st alternative&2nd alternative&lst alternative
&2nd alternative\\ \hline
 K&$(2e)+(2f)$&$(4i)$ &$(2c)+(2d)$&$(4f)$ \\
 Mn&$(2g)$\footnote{The $z$ parameter of these positions is $z\sim\frac{1}{4}$.}
 &$(a)+(b)+(c)+(d)$&$(4e)$&$(2a)+(2b)$\\
 Cl&$(a)+(b)+(c)+(d)$&$(2g)$\footnotemark[1]
 &$(4e)^{\text{a}}$\\
 He&$(8r)^{\text{a}}$&$(4j)^{\text{a}}$&$(4g)^{\text{a}}$\\
 Ag& &$(4k)^{\text{a}}$& &$(4h)^{\text{a}}$\\
\end{tabular}
\end{ruledtabular}
\end{table*}

\begin{table}
\caption{\label{tab:table4}Numbers in columns Three--Five have been
aligned by using the ``d'' column specifier (requires the
\texttt{dcolumn} package). Non-numeric entries (those entries without
a ``.'') in a ``d'' column are aligned on the decimal point. Use the
``D'' specifier for more complex layouts. }
\begin{ruledtabular}
\begin{tabular}{ccddd}
One&Two&\mbox{Three}&\mbox{Four}&\mbox{Five}\\
\hline
one&two&\mbox{three}&\mbox{four}&\mbox{five}\\
He&2& 2.77234 & 45672. & 0.69 \\
C\footnote{Some tables require footnotes.}
  &C\footnote{Some tables need more than one footnote.}
  & 12537.64 & 37.66345 & 86.37 \\
\end{tabular}
\end{ruledtabular}
\end{table}

@@

%\input acknowledgement.tex   % input acknowledgement

\begin{thebibliography}{99}

  \bibitem{d0det}
    Standard D\O\ detector reference:  \\
V.M.~Abazov {\sl et al.} (D0 Collaboration),
Nucl. Instrum. Methods Phys. Res. A {\bf 565}, 463  (2006).

  \bibitem{d0lumi}
    ** New ** D\O\ luminosity reference: \\
T.~Andeen {\sl et al.}, FERMILAB-TM-2365 (2007).

  \bibitem{pdg}
   Particle Data Group reference: \\
   W.-M.~Yao {\sl et al.}, Journal of Physics G {\bf 33}, 1 (2006).

  \bibitem{geant}
    {\sc Geant} reference: \\
    R. Brun and F. Carminati, CERN Program Library Long Writeup W5013, 1993 (unpublished).

  \bibitem{pythia}
    {\sc Pythia} reference: \\
    T. Sj\"{o}strand {\sl et al.}, Comput. Phys. Commun. {\bf 135}, 238 (2001).

  \bibitem{cteq}
    {\sc Cteq6} reference: \\
    J. Pumplin {\sl et al.}, JHEP {\bf 0207} 012 (2002) and
    D. Stump {\sl et al.}, JHEP {\bf 0310} 046 (2003).

  \bibitem{cls}
    LEP CL$_S$ reference: \\
    T. Junk, Nucl. Instrum. Methods A {\bf 434}, 435 (1999).

  \bibitem{d0limit}
   D\O\ Bayesian reference: \\
   I. Bertram {\sl et al.}, FERMILAB-TM-2104 (2000).

  \bibitem{d0jets}
  D\O\ cone-jet reference: \\
G.C.~Blazey {\it et al.}, in
{\sl Proceedings of the Workshop: QCD and Weak Boson
Physics in Run II,} edited by U.~Baur, R.K.~Ellis, and
D. Zeppenfeld, Fermilab-Pub-00/297 (2000).

\end{thebibliography}

>>>>

% The following information is for internal review, please remove them for submission
\widetext
\leftline{Version xx as of \today}
\leftline{Primary authors: Carlos Yero, Werner Boeglin, Mark Jones}
\leftline{To be submitted to PRL}
\leftline{Comment to {\tt cyero002@fiu.edu} by xxx, yyy}
\centerline{\em D\O\ INTERNAL DOCUMENT -- NOT FOR PUBLIC DISTRIBUTION}

@@

\title{First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}}
\input author_list.tex       % D0 authors (remove the first 3 lines
                             % of this file prior to submission, they
                             % contain a time stamp for the authorlist)
                             % (includes institutions and visitors)
\date{\today}

\begin{abstract}
  First results of cross section measurements of the $^{2}H(e,e'p)n$ reaction at momentum transfers \\ 4 $\leq Q^{2}\leq$ 5 (GeV/c)$^{2}$  and
  neutron recoil momenta from 0.460 GeV/c up to 1.14 GeV/c are presented. At the selected kinematics, Meson Exchange Currents (MEC) and Isobar
  Configurations (IC) are suppressed. Final State Interactions have also been suppressed by choosing a kinematic region where the neutron recoil
  angle is between 35 and 45 degrees with respect to the momentum transfer. This suppression was seen in a previous D(e,e'p)n experiment \cite{halla_deut_2011}
  and is also predicted in modern theoretical calculations \cite{sargsian_2015}. In this region, the Plane Wave Impulse Approximation (PWIA) dominates and
  comparisons between measured and predicted cross sections become sensitive to the deuteron momentum distributions.

%  momentum distribution has been determined from measured for neutron recoil momenta up to 1.14 GeV/c.

  %An article usually includes an abstract, a concise summary of the work
%covered at length in the main body of the article. It is used for
%secondary publications and for information retrieval purposes.
%For PRL, the rule of thumb is that the abstract should be less than
%8 lines and the text (excluding authors, abstract but including tables,
%figures and references) should be less than 4 pages (leave about 20 lines
%empty on page 4) in two-column format.
%PRL and PRD papers have to have PACS (Phsyics and Astronomy Classification
%Scheme) numbers. Please see {\tt http://www.aip.org/pacs/} for the numbers
%relevant to your paper. A set of standard references can be found at the
%end of this example paper.
\end{abstract}

@@

@@

\input acknowledgement.tex   % input acknowledgement

\bibliography{prl}
